\section{Current status, use of proceeds and milestones}

\subsection{Current Status and Milestones}
{\it Acknowledgements} is currently in the product development stage, described in the Financing Roadmap. Development of {\it Acknowledgements} will be finished by late-August, which will constitute the ``Start'' Milestone of the Financing Roadmap (Figure \ref{steppingStones}). 

With a complete initial product, the integration of {\it Acknowledgements} into client systems will begin. Upon successful deployment of {\it Acknowledgements}, immediate financial return is expected from clients. Revenue will grow proportionally to the number of clients and their respective projects using {\it Acknowledgements}.

\subsection{Funding and Use of Proceeds}
{\it Acknowledgements} is currently in need of \$2000 in seed money. This will fund small costs associated with setting up a home office. The majority of the funds will pay for web servers to host our product for our first client and any meetings required while liaising with potential clients.

Once {\it Acknowledgements} has been successfully deployed in a live environment, significant resources will be attributed to testing and continuous improvement of features which are not optimized for a live environment. The deployed system will greatly elevate the value of {\it Acknowledgements} and act as a case study for acquiring new clients. 

Depending on initial interest in {\it Acknowledgements}, additional funding for sales and marketing may be required at this stage to further promote {\it Acknowledgements} within the industry. Funds would be used to fund communications and meeting travel expenses to meet with general contractors across Canada to promote the benefits of implementing {\it Acknowledgements}.