\section{The Problem}

\subsection{Market Overview}
The construction industry is a notoriously slow moving and with few exceptions a laggard in the adoption of new technologies. While selling a new product is initially hard in this environment, there is huge potential to expand once ealy adopters have been found and proven the product's value. The Canadian Construction Association estimates the value of all current Canadian building permits to be \$5.85 Billion as of January 2013. While this is an enormous industry, there are still many opportunities to make processes more efficient and greatly increase project profits.

Despite being such a large industry, major general contractors still fail to take full advantage of full electronic document management and approval systems. Instances of completely paper based systems exist across the industry while few companies have migrated to electronic systems which have been utilized in other industries for over a decade. Despite general contractors being responsible for the management of hundred of technical drawings per project, many either fail to make use of electronic document tracking, or rely on management systems developed within the company. While systems developed within a company are highly customizable, these companies simply do not have the capabilities in-house to develop and maintain systems which take advantage of constantly evolving web technology.

\subsection{Market Challenges}

The construction industry is very stable industry which has exhibited significant growth over the past decade despite a slow global economy. Statistics Canada estimates that the value of building permits issued across Canada have grown from \$ 24.5 Million in 1995 to \$ 61 Million in 2009. As the industry and the size of its corporations grow, assuring internal efficiency does not suffer is critical to remaining competitive. It is because of this growth that a system such as {\it Acknowledgements} is critical for large corporations to maintain document approval efficiency across hundreds of concurrent projects.

While large corporations dominate the market, Defence Construction Canada estimated that 90\% of construction firms still employ fewer than 20 people. These firms manage only few projects at any one time, but organizational efficiency is just as critical to these small companies due to their limited resources. With a slow economy hurting industries across Canada, everyone is looking to streamline their internal processes and come out on top.

\subsection{Market Opportunity}
Positioning itself to help a growing industry that is trying to improve efficiency, {\it Acknowledgements} will revolutionize electronic document tracking and approval processes. By migrating processes from traditional paper based systems and bulky in-house developed systems, firms will be able to realize significant improvements in document approval times. The benefits of these efficiencies will greatly outweigh the project based cost of using {\it Acknowledgements}.

Document management is not only a problem for a general contractor, but for all of their dependent partners as well. While a general contractor must coordinate a project, they are constantly managing documents as they move between:

\begin{itemize}
	\item Clients
	\item Architects
	\item Civil Engineers
	\item Sub-contractors
\end{itemize}

Coordinating the movement of these documents and their current status in the approval process is a very complicated and time consuming process. By centralizing the state of each document as it is passed between stakeholders, {\it Acknowledgements} will greatly simplify this process without compromising integrity. This coordination will be performed via a secure web-based application, where each stakeholder will be able to access a unified interface and thus quite literally be ``on the same page''.