\section{Management Team}

The {\it Acknowledgements}  management team is includes two University of Waterloo alumni, with thorough experience working in a variety of technical fields. With very diverse backgrounds, Brock and Karl are able to adapt to a variety of situations with which {\it Acknowledgements} will be confronted.

\subsection{Brock Kopp, Co-founder}
Brock is a University of Waterloo Mechatronics Engineering graduate. Brock has developed a wide variety of process management software applications for a variety of applications. Most notably Brock was the lead developer for a proprietary product management application, used in the Canadian precast concrete industry. This application was capable of managing the production, quality control and yard management procedures of a large scale production facility. Brock has also been a developer for a product lifecycle management system in the publishing industry. This diverse experience will allow Brock to combine best practices from many backgrounds into {\it Acknowledgements}. Brock has also gained practical experience approaching and managing relationship with external corporations through is experience planning and executing a week long orientation event. In this role Brock was able to secure funding from various industrial sources. Brock has a strong financial background, gained through his role as Director for an \$ 11 Million endowment foundation over the past 2 years.

\subsection{Karl Price, Co-founder}
Karl is the driving force behind {\it Acknowledgements}. As a graduate from the University of Waterloo, Karl has extensive experience in product development, gained through his work with the Toronto Sick Children's Hospital. Here Karl lead the development of multiple tools to be used in the medical industry. Looking to broaden his horizons, Karl will use his experience developing in the highly regulated medical industry to further improve the security and quality assurance of {\it Acknowledgements'} processes. Karl has a background built upon many years of web application development . Working on web development projects for Rogers telecommunications and Sears Canada as well as various freelance projects, Karl has gained many contacts in the web development industry which can be leveraged to support the growth of {\it Acknowledgements}.

\subsection{Future Key Hires}
The founders of {\it Acknowledgements} bring extensive technical and industrial background to {\it Acknowledgements}. These technical skills will greatly facilitate the development of an industry leading document management system. While the security, robustness and reliability of {\it Acknowledgements} will be assured with the team of co-founders, further staff will be required to assure that user interface of {\it Acknowledgements} is not only industry leading, but as one of the top web application interfaces in the world.

This will be achieved by hiring a specialist in user-interface design and user testing. This specialist will be responsible for refining the interface of {\it Acknowledgements} in the later phases of development. They will then focus on user testing of the application with users who are both familiar with competing solutions as well as individuals in the construction industry having no experience using document management systems. Testers will be recruited not only from general contracting companies but also from architecture and engineering firms. These testers will be recruited both through potential clients as well as externally through known industry contacts. Once the application has undergone an initial release, this interface specialist will be responsible for ongoing application improvement as well as liaising with current clients to identify and manage software issues.

As further clients are acquired, the executive team is expected to grow to include a VP for client development. This VP will hired with established connection within the construction industry and be responsible for seeking and establishing new clients. This role will become necessary as the number of clients grows to a point where the current staff can no longer effectively maintain relationships with existing clients while seeking new opportunities.